\textsf{Are large language models superhuman chemists?}

### 2024-10-19 src/tex/sections/manually_sources_table.tex
Update manually_sources_table.tex
add 2 more sources

Technical chemistry & Based on notes from lectures at school at the University of Oviedo && 12\\

@@

Physical Chemistry & Based on a textbook & 6\\

@@

>>>>

Technical chemistry & Based on notes from lectures at the University of Oviedo && 12\\

@@

Physical Chemistry & Based on a textbook && 6\\

@@

Analytical Chemistry & Based from exams at IIT Bombay, India && 5\\
Polymer Chemistry & Based on lecture notes from FSU, Jena && 15\\
